Supplementary

### 2021-11-17 Supplymentary.tex
*tab 1

\clearpage
\makeatletter
\efloat@restorefloats
\makeatother

\begin{appendix}
\hypertarget{sa-confirming-the-five-factor-solution-obtained-using-minimum-residual-extraction-method}{%
\section{SA: Confirming the five factor solution obtained using minimum
residual extraction
method}\label{sa-confirming-the-five-factor-solution-obtained-using-minimum-residual-extraction-method}}

@@

Table @ref(tab:tabDesAppB) summarizes the univariate descriptive
statistics for the 48 items with un-merged options. Some of the items
were skewed with high Kurtosis values. Our data violated both univariate
normality (Shapiro-Wilk statistics) and multivariate normality
assumptions {[}Marida's test{]}. Multivariate skew was = 494.70 (p
\textless0.001) and multivariate kurtosis was = 2,705.00 (p
\textless0.001). Due to these violations and ordinal nature of the
response data polychoric correlations over Pearson's correlations was
chosen. Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO)
measures of sampling adequacy. The overall KMO vale for 48 items was
0.65 which was above the cutoff value (.50) indicating a mediocre
sample. Bartlett's test of sphericity, \(\chi^2\) (1128) = 5515.20, p
\textless{} .001 indicated the correlations between items are adequate
for the EFA. However only 4.34\% of the inter-item correlation
coefficients were greater than .30. The absolute value of inter-item
correlation ranged between .00 to .96.Figure @ref(fig:figCorAppB)
depicts the correlation matrix. For un-merged response option Horn's
parallel analysis with 500 iterations indicated a five-factor solution.
However, Scree plot and the MAP method suggested 6-factor solution.
five-factor solution . As a result, we tested both five-factor and
six-factor solutions. The six factor solution yielded a factor with only
two salient loading (Table @ref(tab:EFAsix). Thus we reject the six
factor solution. The five factor solution retained 24 items (Table
@ref(tab:EFATableAppB)). However the factors are less interpretable in
terms of common theme. Thus we reject the five factor solution.

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/facIdFigAppB-1.pdf}
\caption{(\#fig:facIdFigAppB)Factor Identification (A) Parallel analysis
(B) Scree Plot {[}Unmerged response options{]}}
\end{figure}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Five Factor Solution {[}Unmerged Responses{]} (24 Items)}
\end{minipage} \\
\midrule
\endhead
\textbf{F1} \\
I use light therapy applying a blue light box. \\
I use light therapy applying a light visor. \\
I use light therapy applying a white light box. \\
I use light therapy applying another form of light device. \\
I use an alarm with a dawn simulation light. \\
\textbf{F2} \\
I spend more than 3 hours per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I spend 30 minutes or less per day (in total) outside. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
\textbf{F3} \\
I look at my mobile phone screen immediately after waking up. \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I check my phone when I wake up at night. \\
\textbf{F4} \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I seek out knowledge on how to improve my light exposure. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
I discuss the effects of light on my body with other people. \\
I modify my light environment to match my current needs. \\
I dim my room light within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
\textbf{F5} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\bottomrule
\end{longtable}
\end{appendix}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\title{Supplementary}
\author{Mushfiqul Anwar Siraji\textsuperscript{1, *}, Rafael Robert Lazar\textsuperscript{2, 3, *}, Juliëtte van Duijnhoven\textsuperscript{4}, Luc Schlangen\textsuperscript{5}, Shamsul Haque\textsuperscript{1}, Vineetha Kalavally\textsuperscript{6}, Céline Vetter\textsuperscript{7, 8}, Gena Glickman\textsuperscript{9}, Karin Smolders\textsuperscript{10}, \& Manuel Spitschan\textsuperscript{11, 2, 3}}
\date{}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Arial}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Supplementary},
  pdfauthor={Mushfiqul Anwar Siraji1, *, Rafael Robert Lazar2, 3, *, Juliëtte van Duijnhoven4, Luc Schlangen5, Shamsul Haque1, Vineetha Kalavally6, Céline Vetter7, 8, Gena Glickman9, Karin Smolders10, \& Manuel Spitschan11, 2, 3},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{SA}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{3} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{4} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{5} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{6} Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia\\\textsuperscript{7} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{8} Ximes GmbH, Frankfurt, Germany\\\textsuperscript{9} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{10} Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands\\\textsuperscript{11} University of Oxford, Department of Experimental Psychology, Oxford, UK\\\textsuperscript{*} Joint first author}

\begin{document}
\maketitle

\hypertarget{sa-confirming-the-five-factor-solution-obtained-using-minimum-residual-extraction-method}{%
\section{SA: Confirming the five factor solution obtained using minimum residual extraction method}\label{sa-confirming-the-five-factor-solution-obtained-using-minimum-residual-extraction-method}}

@@

Table \ref{tab:tabDesAppB} summarizes the univariate descriptive statistics for the 48 items with un-merged options. Some of the items were skewed with high Kurtosis values. Our data violated both univariate normality (Shapiro-Wilk statistics) and multivariate normality assumptions {[}Marida's test{]}. Multivariate skew was = 494.70 (p \textless0.001) and multivariate kurtosis was = 2,705.00 (p \textless0.001). Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen. Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy. The overall KMO vale for 48 items was 0.65 which was above the cutoff value (.50) indicating a mediocre sample. Bartlett's test of sphericity, \(\chi^2\) (1128) = 5515.20, p \textless{} .001 indicated the correlations between items are adequate for the EFA. However only 4.34\% of the inter-item correlation coefficients were greater than .30. The absolute value of inter-item correlation ranged between .00 to .96.Figure \ref{fig:figCorAppB} depicts the correlation matrix. For un-merged response option Horn's parallel analysis with 500 iterations indicated a five-factor solution. However, Scree plot and the MAP method suggested 6-factor solution. five-factor solution . As a result, we tested both five-factor and six-factor solutions. The six factor solution yielded a factor with only two salient loading (Table \ref{tab:EFAsix}. Thus we reject the six factor solution. The five factor solution retained 24 items (Table \ref{tab:EFATableAppB}). However the factors are less interpretable in terms of common theme. Thus we reject the five factor solution.

@@

\begin{figure}
\centering
\includegraphics{Supplymentary_files/figure-latex/facIdFigAppB-1.pdf}
\caption{\label{fig:facIdFigAppB}Factor Identification (A) Parallel analysis (B) Scree Plot {[}Unmerged response options{]}}
\end{figure}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Five Factor Solution {[}Unmerged Responses{]} (24 Items)}
\end{minipage} \\
\midrule
\endhead
\textbf{F1} \\
I use light therapy applying a blue light box. \\
I use light therapy applying a light visor. \\
I use light therapy applying a white light box. \\
I use light therapy applying another form of light device. \\
I use an alarm with a dawn simulation light. \\
\textbf{F2} \\
I spend more than 3 hours per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I spend 30 minutes or less per day (in total) outside. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
\textbf{F3} \\
I look at my mobile phone screen immediately after waking up. \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I check my phone when I wake up at night. \\
\textbf{F4} \\
I use a blue-filter app on my computer screen within 1 hour before attempting to fall asleep. \\
I seek out knowledge on how to improve my light exposure. \\
I dim my computer screen within 1 hour before attempting to fall asleep. \\
I discuss the effects of light on my body with other people. \\
I modify my light environment to match my current needs. \\
I dim my room light within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
\textbf{F5} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1 hour before attempting to fall asleep. \\
\bottomrule
\end{longtable}

\hypertarget{geographic-locations-of-survey-participants}{%
\section{Geographic Locations of Survey Participants}\label{geographic-locations-of-survey-participants}}

\begingroup\fontsize{8}{10}\selectfont

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{10cm}>{\raggedright\arraybackslash}p{4cm}}
\caption{\label{tab:TzTable}Geographical Location}\\
\toprule
 & **N = 690**\\
\midrule
\endfirsthead
\caption[]{\label{tab:TzTable}Geographical Location \textit{(continued)}}\\
\toprule
 & **N = 690**\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\_\_Time zone - Country\_\_ & \\
United States - America/New\_York (UTC -04:00) & 63 (9.1\%)\\
United Kingdom - Europe/London (UTC) & 57 (8.3\%)\\
Germany - Europe/Berlin (UTC +01:00) & 53 (7.7\%)\\
India - Asia/Kolkata (UTC +05:30) & 38 (5.5\%)\\
\addlinespace
United States - America/Los\_Angeles (UTC -07:00) & 37 (5.4\%)\\
United States - America/Chicago (UTC -05:00) & 30 (4.3\%)\\
France - Europe/Paris (UTC +01:00) & 22 (3.2\%)\\
Switzerland - Europe/Zurich (UTC +01:00) & 21 (3.0\%)\\
Brazil - America/Sao\_Paulo (UTC -03:00) & 19 (2.8\%)\\
\addlinespace
Netherlands - Europe/Amsterdam (UTC +01:00) & 19 (2.8\%)\\
Canada - America/Toronto (UTC -04:00) & 16 (2.3\%)\\
Poland - Europe/Warsaw (UTC +01:00) & 15 (2.2\%)\\
Canada - America/Edmonton (UTC -06:00) & 14 (2.0\%)\\
Finland - Europe/Helsinki (UTC +02:00) & 9 (1.3\%)\\
\addlinespace
Indonesia - Asia/Jakarta (UTC +07:00) & 9 (1.3\%)\\
Italy - Europe/Rome (UTC +01:00) & 9 (1.3\%)\\
Chile - America/Santiago (UTC -03:00) & 8 (1.2\%)\\
Russian Federation - Europe/Moscow (UTC +03:00) & 8 (1.2\%)\\
China - Asia/Shanghai (UTC +08:00) & 7 (1.0\%)\\
\addlinespace
Malaysia - Asia/Kuala\_Lumpur (UTC +08:00) & 7 (1.0\%)\\
Spain - Europe/Madrid (UTC +01:00) & 7 (1.0\%)\\
United States - America/Phoenix (UTC -07:00) & 7 (1.0\%)\\
Canada - America/Vancouver (UTC -07:00) & 6 (0.9\%)\\
New Zealand - Pacific/Auckland (UTC +13:00) & 6 (0.9\%)\\
\addlinespace
Philippines - Asia/Manila (UTC +08:00) & 6 (0.9\%)\\
Turkey - Europe/Istanbul (UTC +03:00) & 6 (0.9\%)\\
United States - America/Denver (UTC -06:00) & 6 (0.9\%)\\
United States - America/Detroit (UTC -04:00) & 6 (0.9\%)\\
Argentina - America/Argentina/Buenos\_Aires (UTC -03:00) & 5 (0.7\%)\\
\addlinespace
Australia - Australia/Melbourne (UTC +11:00) & 5 (0.7\%)\\
Ireland - Europe/Dublin (UTC) & 5 (0.7\%)\\
Lithuania - Europe/Vilnius (UTC +02:00) & 5 (0.7\%)\\
South Africa - Africa/Johannesburg (UTC +02:00) & 5 (0.7\%)\\
Australia - Australia/Brisbane (UTC +10:00) & 4 (0.6\%)\\
\addlinespace
Belgium - Europe/Brussels (UTC +01:00) & 4 (0.6\%)\\
Israel - Asia/Jerusalem (UTC +02:00) & 4 (0.6\%)\\
Sweden - Europe/Stockholm (UTC +01:00) & 4 (0.6\%)\\
United States - America/Boise (UTC -06:00) & 4 (0.6\%)\\
Czech Republic - Europe/Prague (UTC +01:00) & 3 (0.4\%)\\
\addlinespace
Denmark - Europe/Copenhagen (UTC +01:00) & 3 (0.4\%)\\
Germany - Europe/Busingen (UTC +01:00) & 3 (0.4\%)\\
Greece - Europe/Athens (UTC +02:00) & 3 (0.4\%)\\
Iran & 3 (0.4\%)\\
Japan - Asia/Tokyo (UTC +09:00) & 3 (0.4\%)\\
\addlinespace
Norway - Europe/Oslo (UTC +01:00) & 3 (0.4\%)\\
Romania - Europe/Bucharest (UTC +02:00) & 3 (0.4\%)\\
Serbia - Europe/Belgrade (UTC +01:00) & 3 (0.4\%)\\
Slovenia - Europe/Ljubljana (UTC +01:00) & 3 (0.4\%)\\
Taiwan & 3 (0.4\%)\\
\addlinespace
United States - America/Anchorage (UTC -08:00) & 3 (0.4\%)\\
United States - America/Indiana/Indianapolis (UTC -04:00) & 3 (0.4\%)\\
United States - America/Kentucky/Louisville (UTC -04:00) & 3 (0.4\%)\\
Argentina - America/Argentina/Cordoba (UTC -03:00) & 2 (0.3\%)\\
Australia - Australia/Adelaide (UTC +10:30) & 2 (0.3\%)\\
\addlinespace
Australia - Australia/Perth (UTC +08:00) & 2 (0.3\%)\\
Australia - Australia/Sydney (UTC +11:00) & 2 (0.3\%)\\
Brazil - America/Araguaina (UTC -03:00) & 2 (0.3\%)\\
Brazil - America/Bahia (UTC -03:00) & 2 (0.3\%)\\
Canada - America/Moncton (UTC -03:00) & 2 (0.3\%)\\
\addlinespace
Colombia - America/Bogota (UTC -05:00) & 2 (0.3\%)\\
Costa Rica - America/Costa\_Rica (UTC -06:00) & 2 (0.3\%)\\
Croatia - Europe/Zagreb (UTC +01:00) & 2 (0.3\%)\\
Ecuador - America/Guayaquil (UTC -05:00) & 2 (0.3\%)\\
Estonia - Europe/Tallinn (UTC +02:00) & 2 (0.3\%)\\
\addlinespace
Hong Kong - Asia/Hong\_Kong (UTC +08:00) & 2 (0.3\%)\\
Hungary - Europe/Budapest (UTC +01:00) & 2 (0.3\%)\\
Jordan - Asia/Amman (UTC +03:00) & 2 (0.3\%)\\
Latvia - Europe/Riga (UTC +02:00) & 2 (0.3\%)\\
Malaysia - Asia/Kuching (UTC +08:00) & 2 (0.3\%)\\
\addlinespace
Mexico - America/Mexico\_City (UTC -06:00) & 2 (0.3\%)\\
Nepal - Asia/Kathmandu (UTC +05:45) & 2 (0.3\%)\\
Portugal - Europe/Lisbon (UTC) & 2 (0.3\%)\\
Slovakia - Europe/Bratislava (UTC +01:00) & 2 (0.3\%)\\
Spain - Africa/Ceuta (UTC +01:00) & 2 (0.3\%)\\
\addlinespace
Sudan - Africa/Khartoum (UTC +02:00) & 2 (0.3\%)\\
United States - America/Adak (UTC -09:00) & 2 (0.3\%)\\
United States - Pacific/Honolulu (UTC -10:00) & 2 (0.3\%)\\
Viet Nam - Asia/Ho\_Chi\_Minh (UTC +07:00),British - America/Tortola (UTC -04:00) & 2 (0.3\%)\\
Albania - Europe/Tirane (UTC +01:00) & 1 (0.1\%)\\
\addlinespace
Argentina - America/Argentina/Jujuy (UTC -03:00) & 1 (0.1\%)\\
Australia - Antarctica/Macquarie (UTC +11:00) & 1 (0.1\%)\\
Australia - Australia/Darwin (UTC +09:30) & 1 (0.1\%)\\
Austria - Europe/Vienna (UTC +01:00) & 1 (0.1\%)\\
Bangladesh - Asia/Dhaka (UTC +06:00) & 1 (0.1\%)\\
\addlinespace
Brazil - America/Cuiaba (UTC -04:00) & 1 (0.1\%)\\
Brazil - America/Fortaleza (UTC -03:00) & 1 (0.1\%)\\
Bulgaria - Europe/Sofia (UTC +02:00) & 1 (0.1\%)\\
Cameroon - Africa/Douala (UTC +01:00) & 1 (0.1\%)\\
Canada - America/Blanc-Sablon (UTC -04:00) & 1 (0.1\%)\\
\addlinespace
Canada - America/Halifax (UTC -03:00) & 1 (0.1\%)\\
Canada - America/Resolute (UTC -05:00) & 1 (0.1\%)\\
Cayman Islands - America/Cayman (UTC -05:00) & 1 (0.1\%)\\
Chile - Pacific/Easter (UTC -05:00) & 1 (0.1\%)\\
Cyprus - Asia/Famagusta (UTC +02:00) & 1 (0.1\%)\\
\addlinespace
Guatemala - America/Guatemala (UTC -06:00) & 1 (0.1\%)\\
Korea,Republic of - Asia/Seoul (UTC +09:00) & 1 (0.1\%)\\
Macedonia & 1 (0.1\%)\\
Martinique - America/Martinique (UTC -04:00) & 1 (0.1\%)\\
Mexico - America/Monterrey (UTC -06:00) & 1 (0.1\%)\\
\addlinespace
Mongolia - Asia/Ulaanbaatar (UTC +08:00) & 1 (0.1\%)\\
Myanmar - Asia/Yangon (UTC +06:30) & 1 (0.1\%)\\
New Zealand - Pacific/Chatham (UTC +13:45) & 1 (0.1\%)\\
Nigeria - Africa/Lagos (UTC +01:00) & 1 (0.1\%)\\
Pakistan - Asia/Karachi (UTC +05:00) & 1 (0.1\%)\\
\addlinespace
Panama - America/Panama (UTC -05:00) & 1 (0.1\%)\\
Russian Federation - Asia/Barnaul (UTC +07:00) & 1 (0.1\%)\\
Russian Federation - Asia/Novosibirsk (UTC +07:00) & 1 (0.1\%)\\
Russian Federation - Asia/Tomsk (UTC +07:00) & 1 (0.1\%)\\
Russian Federation - Asia/Vladivostok (UTC +10:00) & 1 (0.1\%)\\
\addlinespace
Russian Federation - Asia/Yekaterinburg (UTC +05:00) & 1 (0.1\%)\\
Saudi Arabia - Asia/Riyadh (UTC +03:00) & 1 (0.1\%)\\
Singapore - Asia/Singapore (UTC +08:00) & 1 (0.1\%)\\
Spain - Atlantic/Canary (UTC) & 1 (0.1\%)\\
Tanzania & 1 (0.1\%)\\
\addlinespace
Ukraine - Europe/Kiev (UTC +02:00) & 1 (0.1\%)\\
United States - America/Indiana/Tell\_City (UTC -05:00) & 1 (0.1\%)\\
United States - America/North\_Dakota/Center (UTC -05:00) & 1 (0.1\%)\\
United States - America/North\_Dakota/New\_Salem (UTC -05:00) & 1 (0.1\%)\\
Aland Islands - Europe/Mariehamn (UTC +02:00) & 0 (0\%)\\
\addlinespace
Afghanistan - Asia/Kabul (UTC +04:30) & 0 (0\%)\\
Algeria - Africa/Algiers (UTC +01:00) & 0 (0\%)\\
American Samoa - Pacific/Pago\_Pago (UTC -11:00) & 0 (0\%)\\
Andorra - Europe/Andorra (UTC +01:00) & 0 (0\%)\\
Angola - Africa/Luanda (UTC +01:00) & 0 (0\%)\\
\addlinespace
Anguilla - America/Anguilla (UTC -04:00) & 0 (0\%)\\
Antarctica - Antarctica/Casey (UTC +11:00) & 0 (0\%)\\
Antarctica - Antarctica/Davis (UTC +07:00) & 0 (0\%)\\
Antarctica - Antarctica/DumontDUrville (UTC +10:00) & 0 (0\%)\\
Antarctica - Antarctica/Mawson (UTC +05:00) & 0 (0\%)\\
\addlinespace
Antarctica - Antarctica/McMurdo (UTC +13:00) & 0 (0\%)\\
Antarctica - Antarctica/Palmer (UTC -03:00) & 0 (0\%)\\
Antarctica - Antarctica/Rothera (UTC -03:00) & 0 (0\%)\\
Antarctica - Antarctica/Syowa (UTC +03:00) & 0 (0\%)\\
Antarctica - Antarctica/Troll (UTC) & 0 (0\%)\\
\addlinespace
Antarctica - Antarctica/Vostok (UTC +06:00) & 0 (0\%)\\
Antigua and Barbuda - America/Antigua (UTC -04:00) & 0 (0\%)\\
Argentina - America/Argentina/Catamarca (UTC -03:00) & 0 (0\%)\\
Argentina - America/Argentina/La\_Rioja (UTC -03:00) & 0 (0\%)\\
Argentina - America/Argentina/Mendoza (UTC -03:00) & 0 (0\%)\\
\addlinespace
Argentina - America/Argentina/Rio\_Gallegos (UTC -03:00) & 0 (0\%)\\
Argentina - America/Argentina/Salta (UTC -03:00) & 0 (0\%)\\
Argentina - America/Argentina/San\_Juan (UTC -03:00) & 0 (0\%)\\
Argentina - America/Argentina/San\_Luis (UTC -03:00) & 0 (0\%)\\
Argentina - America/Argentina/Tucuman (UTC -03:00) & 0 (0\%)\\
\addlinespace
Argentina - America/Argentina/Ushuaia (UTC -03:00) & 0 (0\%)\\
Armenia - Asia/Yerevan (UTC +04:00) & 0 (0\%)\\
Aruba - America/Aruba (UTC -04:00) & 0 (0\%)\\
Australia - Australia/Broken\_Hill (UTC +10:30) & 0 (0\%)\\
Australia - Australia/Currie (UTC +11:00) & 0 (0\%)\\
\addlinespace
Australia - Australia/Eucla (UTC +08:45) & 0 (0\%)\\
Australia - Australia/Hobart (UTC +11:00) & 0 (0\%)\\
Australia - Australia/Lindeman (UTC +10:00) & 0 (0\%)\\
Australia - Australia/Lord\_Howe (UTC +11:00) & 0 (0\%)\\
Azerbaijan - Asia/Baku (UTC +04:00) & 0 (0\%)\\
\addlinespace
Bahamas - America/Nassau (UTC -04:00) & 0 (0\%)\\
Bahrain - Asia/Bahrain (UTC +03:00) & 0 (0\%)\\
Barbados - America/Barbados (UTC -04:00) & 0 (0\%)\\
Belarus - Europe/Minsk (UTC +03:00) & 0 (0\%)\\
Belize - America/Belize (UTC -06:00) & 0 (0\%)\\
\addlinespace
Benin - Africa/Porto-Novo (UTC +01:00) & 0 (0\%)\\
Bermuda - Atlantic/Bermuda (UTC -03:00) & 0 (0\%)\\
Bhutan - Asia/Thimphu (UTC +06:00),Plurinational State of - America/La\_Paz (UTC -04:00) & 0 (0\%)\\
Bolivia,Sint Eustatius and Saba - America/Kralendijk (UTC -04:00) & 0 (0\%)\\
Bonaire & 0 (0\%)\\
\addlinespace
Bosnia and Herzegovina - Europe/Sarajevo (UTC +01:00) & 0 (0\%)\\
Botswana - Africa/Gaborone (UTC +02:00) & 0 (0\%)\\
Brazil - America/Belem (UTC -03:00) & 0 (0\%)\\
Brazil - America/Boa\_Vista (UTC -04:00) & 0 (0\%)\\
Brazil - America/Campo\_Grande (UTC -04:00) & 0 (0\%)\\
\addlinespace
Brazil - America/Eirunepe (UTC -05:00) & 0 (0\%)\\
Brazil - America/Maceio (UTC -03:00) & 0 (0\%)\\
Brazil - America/Manaus (UTC -04:00) & 0 (0\%)\\
Brazil - America/Noronha (UTC -02:00) & 0 (0\%)\\
Brazil - America/Porto\_Velho (UTC -04:00) & 0 (0\%)\\
\addlinespace
Brazil - America/Recife (UTC -03:00) & 0 (0\%)\\
Brazil - America/Rio\_Branco (UTC -05:00) & 0 (0\%)\\
Brazil - America/Santarem (UTC -03:00) & 0 (0\%)\\
British Indian Ocean Territory - Indian/Chagos (UTC +06:00) & 0 (0\%)\\
Brunei Darussalam - Asia/Brunei (UTC +08:00) & 0 (0\%)\\
\addlinespace
Burkina Faso - Africa/Ouagadougou (UTC) & 0 (0\%)\\
Burundi - Africa/Bujumbura (UTC +02:00) & 0 (0\%)\\
Cambodia - Asia/Phnom\_Penh (UTC +07:00) & 0 (0\%)\\
Canada - America/Atikokan (UTC -05:00) & 0 (0\%)\\
Canada - America/Cambridge\_Bay (UTC -06:00) & 0 (0\%)\\
\addlinespace
Canada - America/Creston (UTC -07:00) & 0 (0\%)\\
Canada - America/Dawson (UTC -07:00) & 0 (0\%)\\
Canada - America/Dawson\_Creek (UTC -07:00) & 0 (0\%)\\
Canada - America/Fort\_Nelson (UTC -07:00) & 0 (0\%)\\
Canada - America/Glace\_Bay (UTC -03:00) & 0 (0\%)\\
\addlinespace
Canada - America/Goose\_Bay (UTC -03:00) & 0 (0\%)\\
Canada - America/Inuvik (UTC -06:00) & 0 (0\%)\\
Canada - America/Iqaluit (UTC -04:00) & 0 (0\%)\\
Canada - America/Nipigon (UTC -04:00) & 0 (0\%)\\
Canada - America/Pangnirtung (UTC -04:00) & 0 (0\%)\\
\addlinespace
Canada - America/Rainy\_River (UTC -05:00) & 0 (0\%)\\
Canada - America/Rankin\_Inlet (UTC -05:00) & 0 (0\%)\\
Canada - America/Regina (UTC -06:00) & 0 (0\%)\\
Canada - America/St\_Johns (UTC -02:30) & 0 (0\%)\\
Canada - America/Swift\_Current (UTC -06:00) & 0 (0\%)\\
\addlinespace
Canada - America/Thunder\_Bay (UTC -04:00) & 0 (0\%)\\
Canada - America/Whitehorse (UTC -07:00) & 0 (0\%)\\
Canada - America/Winnipeg (UTC -05:00) & 0 (0\%)\\
Canada - America/Yellowknife (UTC -06:00) & 0 (0\%)\\
